---
title: "p8105_hw1_yl4606"
author: "Yubei Liang"
date: "9/16/2020"
output: github_document
---

This is my solution to HW1.

```{r package, message=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

## Problem 1 

1. Create a data frame with the specified elements.

```{r dataframe, warning=FALSE}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
```

2. Take the mean of each variable in my data frame.

```{r mean, warning=FALSE}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

Therefore, I cannot take the mean of character and factor variables. Let's try to transform variables in the data frame to numeric.

```{r as.numeric, warning=FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

The character vector cannot be transformed to numeric, and factor vector is transformed to meaningless numbers. So I think that is why their mean cannot be calculated.

3. Convert logical vector to other data types and then do multiplication.

```{r logical_vector, warning=FALSE}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```



## Problem 2

1. This 'penguins' dataset records variables of Antarctica penguins including `r ls(penguins)`. The values of these variable are summarized as below: Those penguins can be categorized into species `r levels(pull(penguins, species))`. They live in distinct islands `r levels(pull(penguins, island))`. The bill length range is `r range(pull(penguins, bill_length_mm), na.rm = T)` in mm, bill depth range is `r range(pull(penguins, bill_depth_mm), na.rm = T)` in mm and flipper length range is `r range(pull(penguins, flipper_length_mm), na.rm = T)` in mm. Body mass range is `r range(pull(penguins, body_mass_g), na.rm = T)` in grams. The data has `r nrow(penguins)` rows and `r ncol(penguins)` columns. The year range is `r range(pull(penguins, year), na.rm = T)`. The sex includes `r levels(pull(penguins, sex))`. The mean of flipper length is `r mean(pull(penguins,flipper_length_mm),na.rm=T)` mm (two rows of NA are removed).

2. Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x).

```{r scatterplot, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("penguins_scatter_plot.pdf", height = 4, width = 6)
```

